\textbf{Computational Fuzzy Extractors}

### 2013-05-17 trunk/CompFuzzExt.tex
Changes to decoding talk

\subsection{Efficiency of \consref{cons:informal construction}}
\label{sec:time main construction}
%\subsection{Analysis of Construction~\ref{cons:LWESecureSketch}}
\consref{cons:informal construction} is only useful if $\decode_t$ can be efficiently implemented.  We now present a particular $\decode_t$ and consider its efficiency:

>>>>

\subsection{Efficiency of \consref{cons:informal construction}}
\label{sec:time main construction}
%\subsection{Analysis of Construction~\ref{cons:LWESecureSketch}}
\consref{cons:informal construction} is only useful if $\decode_t$ can be efficiently implemented.  We need a decoding algorithm for a random linear code with $t$ errors that runs in polynomial time.  We present a simple $\decode_t$.  Replacing our algorithm  with a state of the art algorithm will only increase our correcting capability and improve \consref{cons:informal construction}.
